\textsc{Does Copyright Affect Reuse?\\ Evidence from Wikipedia and the Google Books Digitization Project}

### 2016-09-13 writing/paper.tex
caveated traffic results

Table \ref{tab:traf} reports estimates from such an analysis. Models (1) and (2) include year fixed effects, while Model (3) includes separate year-trends for each of the 4 player quality quartiles. Similarly, Models (2) and (3) also include additional player-page level fixed effects. The estimates in Column (2) indicate that on average, out-of-copyright pages receive a boost of about 20 hits per month after controlling for player and year fixed effects. The coefficient reduces slightly when \emph{$quality \times year$} fixed effects are included. Against a mean of about 101 page-views per month, this represents an increase of about 20\%. In the appendix, I examine the robustness of these estimates to log models. Columns (3) and (4) of Table \ref{tab:app_traf_robust} estimate the impact of copyright on traffic to be about 88.8\%, or twice as large as the OLS estimates. However, a conservative estimate of the impact of copyright on traffic to affected pages would be to boost page-views in the order of 20\%, a significant difference.

>>>>

Table \ref{tab:traf} reports estimates from such an analysis. Models (1) and (2) include year fixed effects, while Model (3) includes separate year-trends for each of the 4 player quality quartiles. Similarly, Models (2) and (3) also include additional player-page level fixed effects. The estimates in Column (2) indicate that on average, out-of-copyright pages receive a boost of about 20 hits per month after controlling for player and year fixed effects. The coefficient reduces slightly when \emph{$quality \times year$} fixed effects are included. Against a mean of about 101 page-views per month, this represents an increase of about 20\%. These results should be interpreted cautiously because given the limited data from the pre-digitization period, it is difficult to validate the parallel trends assumption. Given this issue, in the appendix, I examine the robustness of these estimates to log models using a cross-sectional specification. Columns (3) and (4) of Table \ref{tab:app_traf_robust} estimate the impact of copyright on traffic to be about 88.8\%, or twice as large as the OLS estimates. However, a conservative estimate of the impact of copyright on traffic to affected pages would be to boost page-views in the order of 20\%, a significant difference.
